Cloud Supercomputing

### 2019-05-03 writing/paper/paper.tex
Improve results chapter.

\keywords{\aderdg{}  \and Navier-Stokes \and Another keyword.}
\end{abstract}
\section{Introduction}
In this paper we address the resolution of basic cloud formation processes on modern super computer systems.
%%of convective processes in the context of numerical weather prediction (\textsc{nwp}) on modern super computer systems.
The simulation of cloud formations, as part of convective processes, is expected to play an important role in future numerical weather prediction~\cite{bauer2015quiet}.
%% Numerical weather prediction (\textsc{nwp}) contains processes of different spatio-temporal scales.
%% An important part of future \textsc{nwp} models will be the the resolution of convective processes~\cite{bauer2015quiet}.
This requires both suitable physical models and effective computational realisations. 
Here we focus on the simulation of simple benchmark scenarios~\cite{giraldo2008study}.
These relatively small scale effects are well approximated with the compressible Navier-Stokes equations.
We use the \aderdg{} method of~\cite{dumbser2008unified}, which allows us to simulate the Naview-Stokes equations with a space-time-discretization of arbitrary high order.
In contrast to Runge-Kutta time integrators or semi-implicit methods, an increase of the order of \aderdg{} only results in larger computational kernels and does not affect the complexity of the scheme.
Additionally \aderdg{} is a communication avoiding scheme and reduces the overhead on larger scale.
We see our scheme in the regime of already established methods for cloud simulations, as seen for example in~\cite{giraldo2008study,muller2010adaptive,muller2018strong}.
%%The general approach is to use a space-discretized by higher order Galerkin method, as seen for example in~\cite{giraldo2008study,muller2010adaptive,muller2018strong}.
%%They are often space-discretized by higher order Galerkin methods, as seen for example in~\cite{giraldo2008study,muller2010adaptive,muller2018strong}.
%%Even though all of these implementations use a discretization with a (theoretical) unlimited space-order, they use Runge-Kutta time integrators or semi-implicit methods.
%%It is well known that Runge-Kutta methods become more ineffecient for very high orders.
%%Furthermore, they and the implicit methods are more communication-intensive and thus require a larger overhead and are more complicated to scale.
%%We follow a different approach in this paper and use the \aderdg{} method of~\cite{dumbser2008unified} to simulate various computational fluid dynamics (\textsc{cfd}) scenarios with a focus on flows with stratified flows.

@@

Many realistic atmospheric flows can be described by a perturbation over a background state that is in hydrostatic equilibrium\todo{Mention source}
\newcommand{\backgroundPressure}{\overline{\pressure}}
\newcommand{\backgroundRho}{\overline{\Qrho}}
\begin{equation}
  \label{eq:hydrostatic-balance}
  \pdv{}{z} \backgroundPressure{\left (z \right )} = -g \backgroundRho(z),
\end{equation}
i.e.\ a state, where the pressure gradient is exactly in balance with the gravitational source term $\source[\Qj] = - \bm{k} \Qrho g$.
The vector $\bm{k}$ is the unit vector pointing in $z$-direction.
The momentum equation is dominated by the background flow in this case.
Because this can lead to numerical instabilities, problems of this kind are challenging and require some care.
To lessen the impact of this, we split the pressure $\pressure = \backgroundPressure + \pressure'$ into a sum of the background pressure $\backgroundPressure(z)$ and perturbation $\pressure'(\bm{x}, t)$.
We split the density $\Qrho = \backgroundRho + \Qrho'$ in the same manner and arrive at
\begin{equation}
  \label{eq:momentum-equation-split}
  \pdv{\Qj}{t}+ \divergence{ \left(
    \Qv \otimes \Qj + \bm{I} \pressure'
    \right)
  } + \viscFlux_\Qj
  =
  -g \bm{k} \Qrho'.
\end{equation}
Note that a similar and more complex splitting is performed in~\cite{muller2010adaptive,giraldo2008study}.
In contrast to this, we use the true compressible Navier-Stokes equations with minimal modifications.
\section{Numerics}
\todo{LR: Hier würde ich noch ein paar einleitende Worte hinzufügen}
We use an \aderdg{}-scheme and a \muscl{} finite volume method.
Both can be considered as instances of the more general \textsc{PnPm} schemes of~\cite{dumbser2008unified}.
We use a Rusanov-style flux that is adapted to \pde{}s with viscous terms~\cite{gassner2008discontinuous,fambri2017space}.
The finite volume scheme is stabilized with the van Albada limiter\todo{Cite vanalbada}.

@@

\begin{figure}[htb]
  \centering
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \includegraphics{paper_lid_driven_cavity}
    \caption{\label{fig:cavity-flow}Our approximation (lines) of the lid-driven cavity flow vs.\ reference solution (markers) of~\cite{ghia1982high}.}
  \end{subfigure}~%
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \includegraphics{paper_abc_flow_velocity}
    \caption{\label{fig:abc-flow}\textsc{abc}-flow. We show the velocity in $x$-direction for slices through the domain, where all but the mentioned coordinates are held constant at a value of zero.
    The analytical solution is represented by lines, the numerical results by markers.}
  \end{subfigure}
  \caption{\textsc{cfd} scenarios}
  \label{fig:cdf-results}
\end{figure}

@@

@@

Let
\begin{equation}
  \label{eq:radius}
  r^2 = \Vert \bm{x} - \bm{x_c} \Vert_2 %(x - x_0)^2 + (z - z_0)^2
\end{equation}
denote the Euclidian distance between the spatial positions $\bm{x} = x, z$ and the center of a bubble $\bm{x_c} = x_c, z_c$.
In case of three-dimensional scenarios the vectors $\bm{x}$ and $\bm{x_c}$ also contain a y coordinate.
For our first scenario, the cosine bubble, we use a pertubation of the form
\begin{align}
  \label{eq:cos-pertubation}
  \pertubationPotT &= \begin{cases}
    \nicefrac{A}{2} \left[ 1 + \cos(\pi r) \right] & r \leq a, \\
    0 & r > a,
    \end{cases}
\end{align}
where $A$ denotes the maximal perturbation and $a$ is the size of the bubble.
We use the constants
\begin{equation}\label{eq:cosine-bubble}
  A = \SI{0.5}{\K} \quad a = \SI{250}{\m} \quad x_c = \SI{500}{\m} \quad z_c = \SI{350}{\m}.
\end{equation}
For the three-dimensional bubble, we set $y_c = x_c = \SI{500}{\m}$ and lower the bubble to $z_c = \SI{260}{\m}$.
We use a constant viscosity of $\mu = 0.01$ and a simulation time of $\SI{400}{\s}$ for 3D and $\SI{600}{\s}$ for 2D\todo{viscosity for 3D?}.
We specialize the \amr{}-criterion~\pcref{eq:refinement-criterion} to our stratified flows by using the potential temperature.

\begin{figure}[htb]
  \centering
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \includegraphics[width=\textwidth]{paper_cosine_bubble}
    \caption{2D Cosine Bubble}
  \end{subfigure}~%
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \includegraphics[width=\textwidth]{paper_cosine_bubble}
    \caption{3D Cosine Bubble}
  \end{subfigure}
  \caption{Cosine Bubble Scenarios}
  \label{fig:cosine-bubbles-results}
\end{figure}

For our second scenario, the colliding bubbles~\cite{muller2010adaptive}, we use perturbations of the form
\begin{equation}
  \label{eq:bubbles-pertubation}
  \pertubationPotT =
  \begin{cases}
    A & r \leq a, \\
    A \exp \left( - \frac{(r-a)^2}{s^2} \right) & r > a,
    \end{cases}
\end{equation}
where $s$ is the decay rate and $r$  is the radius to the center~\pcref{eq:radius}.
We have two bubbles, with constants
\begin{equation}
  \label{eq:bubbles-values}
\begin{alignedat}{6}
  & \text{warm:} \qquad && A = \SI{0.5}{\K}, \quad&& a = \SI{150}{\m}, \quad&& s = \SI{50}{\m}, \quad&& x_c = \SI{500}{\m,} \quad&& z_c = \SI{300}{\m},\\
  & \text{cold:} \qquad && A = \SI{-0.15}{\K}, \quad&& a = \SI{0}{\m}, \quad&& s = \SI{50}{\m}, \quad&& x_c = \SI{560}{\m}, \quad&& z_c = \SI{640}{\m}.
  \end{alignedat}
\end{equation}
Similar to~\cite{muller2010adaptive} and to the previous scenario, we use a constant viscosity of $\mu = 0.01$ to regularize the solution\todo{We use lower visc!}.
We ran this scenario twice, firstly without \amr{} and a mesh of size $\SI{1000/81}{\m} = \SI{12.35}{\m}$.
For the second run we used \amr{} with two adaptive refinement levels and parameters $\Trefine = 2.5$ and $\Tdelete = -0.5$.
This resulted in a mesh with cell sizes lengths of ca. $\SI{111.1}{\m}, \SI{37.04}{\m}, \SI{12.34}{\m}$ up to.
The resulting mesh can be observed in \cref{fig:two-bubbles-ader}.
We observed that even though both results are nearly identical, the \amr{} run managed to use only 1953 cells, instead of 6561 cells for the fully refined solution. 
% points: 70308, 23619
We further want to emphasize that our \amr{}-criterion is able to accurately track the position of the edges of cloud instead of only its position.
This is the main advantage of our gradient-based method in contrast to methods working directly with the value of the solution, as for example~\cite{muller2010adaptive}.
Overall, our result for this benchmark shows an excellent agreement to the previous solutions of~\cite{muller2010adaptive,giraldo2008study}\todo{Is coll.\ bubble contained in se study?}.

In addition, we simulated the same scenario with our \muscl{} method, using $3^2$ patches with $80^2$ finite volume cells each~\todo{check}.
As we use limiting, we do not need any viscosity.
The results of this method (\cref{fig:two-bubbles-fv}) also agree with the reference.
Note that the numerical dissapitivity of the finite volume scheme has a smoothing effect that is similar to the smoothing caused by viscosity.
\begin{figure}[htb]
  \centering
  \begin{subfigure}[t]{0.8\textwidth}
    \centering
    \includegraphics[width=\textwidth]{paper_two_bubbles}
    \caption{\label{fig:two-bubbles-ader}Colliding Bubbles \aderdg{}}
  \end{subfigure}~%
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \includegraphics{paper_lid_driven_cavity}
    \caption{\label{fig:two-bubbles-fv}Colliding Bubbles \muscl{}}
  \end{subfigure}
  \caption{Cosine Bubble Scenarios}
  \label{fig:two-bubbles-results}
\end{figure}

\section{Conclusion}
We presented our implementation of an \aderdg{}-method and a \muscl{}-scheme with \amr{} for the Navier-Stokes equations.
Our implementation is capable of simulating different scenarios:
\begin{itemize}
\item We evaluated our method for standard \textsc{cfd} scenarios and achieved competitive results for all used scenarios.
  This is true for both two-dimensional scenarios (Taylor-Green vortex and lid-driven cavity) and for the three-dimensional \textsc{abc}-flow.
\item Furthermore, our method allows us to simulate flows in hydrostatic equilibrium correctly as our results for the cosine and colliding bubble scenarios showed.
\item We showed that our \amr{}-criterion is able to vastly reduce the number of grid cells while preserving the quality of the results.
\end{itemize}
\todo{LK: Flesh this out a tiny bit, mention properties of \amr{} criterion}

\subsection*{Acknowledgements}
Lukas Krenz was funded by ChEESE (823844), Leonhard Rannabauer was funded by ExaHyPE (671698).
\todo{LK: Standard sentence is: This research was funded by the European Union’s Horizon 2020 Research and Innovation Programme under the project ExaHyPE, grant no.  671698 (call FETHPC-1-2014).
Special thanks goes to Dominic E.\ Charrier who provided help with the implementation in the %\exahypeegine{}.
Also LRZ?}

>>>>

\keywords{\aderdg{}  \and Navier-Stokes \and Another keyword.}
\end{abstract}
\section{Introduction}
In this paper we address the resolution of basic cloud formation processes on modern super computer systems.
%%of convective processes in the context of numerical weather prediction (\textsc{nwp}) on modern super computer systems.
The simulation of cloud formations, as part of convective processes, is expected to play an important role in future numerical weather prediction~\cite{bauer2015quiet}.
%% Numerical weather prediction (\textsc{nwp}) contains processes of different spatio-temporal scales.
%% An important part of future \textsc{nwp} models will be the the resolution of convective processes~\cite{bauer2015quiet}.
This requires both suitable physical models and effective computational realisations. 
Here we focus on the simulation of simple benchmark scenarios~\cite{giraldo2008study}.
They contain relatively small scale effects which are well approximated with the compressible Navier-Stokes equations.
We use the \aderdg{} method of~\cite{dumbser2008unified}, which allows us to simulate the Naview-Stokes equations with a space-time-discretization of arbitrary high order.
In contrast to Runge-Kutta time integrators or semi-implicit methods, an increase of the order of \aderdg{} only results in larger computational kernels and does not affect the complexity of the scheme.
Additionally, \aderdg{} is a communication avoiding scheme and reduces the overhead on larger scale.
We see our scheme in the regime of already established methods for cloud simulations, as seen for example in~\cite{giraldo2008study,muller2010adaptive,muller2018strong}.
%%The general approach is to use a space-discretized by higher order Galerkin method, as seen for example in~\cite{giraldo2008study,muller2010adaptive,muller2018strong}.
%%They are often space-discretized by higher order Galerkin methods, as seen for example in~\cite{giraldo2008study,muller2010adaptive,muller2018strong}.
%%Even though all of these implementations use a discretization with a (theoretical) unlimited space-order, they use Runge-Kutta time integrators or semi-implicit methods.
%%It is well known that Runge-Kutta methods become more ineffecient for very high orders.
%%Furthermore, they and the implicit methods are more communication-intensive and thus require a larger overhead and are more complicated to scale.
%%We follow a different approach in this paper and use the \aderdg{} method of~\cite{dumbser2008unified} to simulate various computational fluid dynamics (\textsc{cfd}) scenarios with a focus on flows with stratified flows.

@@

Many realistic atmospheric flows can be described by a perturbation over a background state that is in hydrostatic equilibrium\todo{Mention source}
\newcommand{\backgroundPressure}{\overline{\pressure}}
\newcommand{\backgroundRho}{\overline{\Qrho}}
\begin{equation}
  \label{eq:hydrostatic-balance}
  \pdv{}{z} \backgroundPressure{\left (z \right )} = -g \backgroundRho(z),
\end{equation}
i.e.\ a state, where the pressure gradient is exactly in balance with the gravitational source term $\source[\Qj] = - \bm{k} \Qrho g$.
The vector $\bm{k}$ is the unit vector pointing in $z$-direction.
The momentum equation is dominated by the background flow in this case.
Because this can lead to numerical instabilities, problems of this kind are challenging and require some care.
To lessen the impact of this, we split the pressure $\pressure = \backgroundPressure + \pressure'$ into a sum of the background pressure $\backgroundPressure(z)$ and perturbation $\pressure'(\bm{x}, t)$.
We split the density $\Qrho = \backgroundRho + \Qrho'$ in the same manner and arrive at
\begin{equation}
  \label{eq:momentum-equation-split}
  \pdv{\Qj}{t}+ \divergence{ \left(
    \Qv \otimes \Qj + \bm{I} \pressure'
    \right)
  } + \viscFlux_\Qj
  =
  -g \bm{k} \Qrho'.
\end{equation}
Note that a similar and more complex splitting is performed in~\cite{muller2010adaptive,giraldo2008study}.
In contrast to this, we use the true compressible Navier-Stokes equations with minimal modifications.
\section{Numerics}
\todo{LR: Hier würde ich noch ein paar einleitende Worte hinzufügen}
We use an \aderdg{}-scheme and a \muscl{} finite volume method.
Both can be considered as instances of the more general \textsc{PnPm} schemes of~\cite{dumbser2008unified}.
We use a Rusanov-style flux that is adapted to \pde{}s with viscous terms~\cite{gassner2008discontinuous,fambri2017space}.
The finite volume scheme is stabilized with the van Albada limiter~\cite{van1997comparative}.

@@

\begin{figure}[htb]
  \centering
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \includegraphics{paper_lid_driven_cavity}
    \caption{\label{fig:cavity-flow}Our approximation (lines) of the lid-driven cavity flow vs.\ reference solution (markers) of~\cite{ghia1982high}.}
  \end{subfigure}~%
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \includegraphics{paper_taylor_green_vel}
    \caption{\label{fig:taylor-green}Taylor green, velocity slices.}

    %\includegraphics{paper_abc_flow_velocity}
    %\caption{\label{fig:abc-flow}\textsc{abc}-flow. We show the velocity in $x$-direction for slices through the domain, where all but the mentioned coordinates are held constant at a value of zero.
    %The analytical solution is represented by lines, the numerical results by markers.}
  \end{subfigure}
  \caption{Two dimensional \textsc{cfd} scenarios}
  \label{fig:cdf-results}
\end{figure}

@@

\begin{figure}[tb]
\centering
\begin{minipage}{.5\textwidth}
  \centering
    \includegraphics{paper_abc_flow_velocity}
    \captionof{figure}{\label{fig:abc-flow}Our approximation (lines) of the lid-driven cavity flow vs.\ reference solution (markers) of~\cite{ghia1982high}.}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
    \includegraphics[width=\textwidth]{paper_two_bubbles_fv}
    \captionof{figure}{\label{fig:two-bubbles-fv}%
    Colliding bubbles with \muscl{}}
\end{minipage}
\end{figure}

@@

Let
\begin{equation}
  \label{eq:radius}
  r^2 = \Vert \bm{x} - \bm{x_c} \Vert_2 %(x - x_0)^2 + (z - z_0)^2
\end{equation}
denote the Euclidian distance between the spatial positions $\bm{x} = x, z$ and the center of a bubble $\bm{x_c} = x_c, z_c$.
In case of three-dimensional scenarios the vectors $\bm{x}$ and $\bm{x_c}$ also contain a y coordinate.

Our first scenario is the colliding bubbles scenario~\cite{muller2010adaptive}.
We use perturbations of the form
\begin{equation}
  \label{eq:bubbles-pertubation}
  \pertubationPotT =
  \begin{cases}
    A & r \leq a, \\
    A \exp \left( - \frac{(r-a)^2}{s^2} \right) & r > a,
    \end{cases}
\end{equation}
where $s$ is the decay rate and $r$  is the radius to the center~\pcref{eq:radius}.
We have two bubbles, with constants
\begin{equation}
  \label{eq:bubbles-values}
\begin{alignedat}{6}
  & \text{warm:} \qquad && A = \SI{0.5}{\K}, \quad&& a = \SI{150}{\m}, \quad&& s = \SI{50}{\m}, \quad&& x_c = \SI{500}{\m,} \quad&& z_c = \SI{300}{\m},\\
  & \text{cold:} \qquad && A = \SI{-0.15}{\K}, \quad&& a = \SI{0}{\m}, \quad&& s = \SI{50}{\m}, \quad&& x_c = \SI{560}{\m}, \quad&& z_c = \SI{640}{\m}.
  \end{alignedat}
\end{equation}
Similar to~\cite{muller2010adaptive}, we use a constant viscosity of $\mu = 0.01$ to regularize the solution.
Note that we use a different implementation of viscosity than~\cite{muller2010adaptive}.
Hence, it is difficult to compare the parametrization directly.
We ran this scenario twice, firstly without \amr{} and a mesh of size $\SI{1000/81}{\m} = \SI{12.35}{\m}$.
For the second run we used \amr{} with two adaptive refinement levels and parameters $\Trefine = 2.5$ and $\Tdelete = -0.5$.
We specialize the \amr{}-criterion~\pcref{eq:refinement-criterion} to our stratified flows by using the potential temperature.
This resulted in a mesh with cell sizes lengths of ca. $\SI{111.1}{\m}, \SI{37.04}{\m}, \SI{12.34}{\m}$.
The resulting mesh can be observed in \cref{fig:two-bubbles-ader}.
We observed that even though both results are nearly identical, the \amr{} run managed to use only 1953 cells, instead of 6561 cells for the fully refined solution. 
% points: 70308, 23619
We further want to emphasize that our \amr{}-criterion is able to accurately track the position of the edges of cloud instead of only its position.
This is the main advantage of our gradient-based method in contrast to methods working directly with the value of the solution, as for example~\cite{muller2010adaptive}.
Overall, our result for this benchmark shows an excellent agreement to the previous solutions of~\cite{muller2010adaptive,giraldo2008study}\todo{Is coll.\ bubble contained in se study?}.

In addition, we simulated the same scenario with our \muscl{} method, using $3^2$ patches with $80^2$ finite volume cells each~\todo{check}.
As we use limiting, we do not need any viscosity.
The results of this method (\cref{fig:two-bubbles-fv}) also agree with the reference.
Note that the numerical dissapitivity of the finite volume scheme has a smoothing effect that is similar to the smoothing caused by viscosity.

For our second scenario, the cosine bubble, we use a pertubation of the form
\begin{align}
  \label{eq:cos-pertubation}
  \pertubationPotT &= \begin{cases}
    \nicefrac{A}{2} \left[ 1 + \cos(\pi r) \right] & r \leq a, \\
    0 & r > a,
    \end{cases}
\end{align}
where $A$ denotes the maximal perturbation and $a$ is the size of the bubble.
We use the constants
\begin{equation}\label{eq:cosine-bubble}
  A = \SI{0.5}{\K} \quad a = \SI{250}{\m} \quad x_c = \SI{500}{\m} \quad z_c = \SI{350}{\m}.
\end{equation}
For the three-dimensional bubble, we set $y_c = x_c = \SI{500}{\m}$ and lower the bubble to $z_c = \SI{260}{\m}$.
This corresponds to the parameters used in~\cite{kelly2012continuous}.
For the 2D case, we use a constant viscosity of $\mu = 0.01$, an \aderdg{}-method of order 5 with two levels of dynamic \amr{}, resulting again in cell sizes of roughly $\SI{111.1}{\m}, \SI{37.04}{\m}, \SI{12.34}{\m}$.
We use slightly different \amr{} parameters of $\Trefine = 1.5$ and $\Tdelete = -0.5$ and let the simulation run for \SI{600}{\s}.
Note that, as seen in \cref{fig:cosine-2d}, our \amr{}-criterion tracks the wavefront of the cloud accurately.
This result shows an excellent agreement to the ones achieved in~\cite{giraldo2008study}\todo{correct source?}.

For the 3D case, we use an \aderdg{}-scheme of order 3 with a static mesh with cell sizes of \SI{40}{\m}. and a shorter simulation duration of \SI{400}{\s}.
Due to the relatively coarse resolution and the hence increased aliasing errors, we need to increase the viscosity to $\mu = 0.02$.
This corresponds to a larger amount of smoothing.
Our results (\cref{fig:cosine-3d}) capture the overall dynamics of the scenario well, similar to the reference solution of~\cite{kelly2012continuous}.

We again use a constant viscosity of $\mu = 0.01$ for the 2D case, and a viscosity of $\mu = 0.02$ for the 3D case.
The simulations run for a time of $\SI{600}{\s}$ and $\SI{400}{\s}$ for two and three-dimensional scenarios respectively.

\begin{figure}[htb]
  \centering
  \includegraphics[width=1.0\textwidth]{paper_two_bubbles}
  \caption{\label{fig:two-bubbles-ader}Colliding Bubbles \aderdg{}}
\end{figure}

\begin{figure}[htb]
  \centering
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \includegraphics[width=\textwidth]{paper_cosine_bubble}
    \caption{\label{fig:cosine-2d}2D Cosine Bubble}
  \end{subfigure}~%
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \includegraphics[width=\textwidth]{paper_cosine_bubble_3d}
    \caption{3D Cosine Bubble}
  \end{subfigure}
  \caption{\label{fig:cosine-3d}Cosine Bubble Scenarios}
  \label{fig:cosine-bubbles-results}
\end{figure}

\section{Conclusion}
We presented our implementation of an \aderdg{}-method and a \muscl{}-scheme with \amr{} for the Navier-Stokes equations.
Our implementation is capable of simulating different scenarios:\todo{LK: Flesh this out a tiny bit, mention properties of \amr{} criterion}
\begin{itemize}
\item We evaluated our method for standard \textsc{cfd} scenarios and achieved competitive results for all used scenarios.
  This is true for both two-dimensional scenarios (Taylor-Green vortex and lid-driven cavity) and for the three-dimensional \textsc{abc}-flow.
\item Furthermore, our method allows us to simulate flows in hydrostatic equilibrium correctly as our results for the cosine and colliding bubble scenarios showed.
\item We showed that our \amr{}-criterion is able to vastly reduce the number of grid cells while preserving the quality of the results.
\end{itemize}

\subsection*{Acknowledgements}
Leonhard Rannabauer was funded by the European Union’s Horizon 2020 Research and Innovation Programme under the project ExaHyPE, grant no.  671698 (call FETHPC-1-2014)
Lukas Krenz  the European Union’s Horizon 2020 Research and Innovation Programme under the project ChEESE, grant no.\ 823844.
Special thanks goes to Dominic E.\ Charrier who provided help with the implementation in the \exahypeengine{}.
\todo{Are those ack.\ correct, esp. call no.\ for Cheese? Also thank lrz?}
